Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-09-30 WSSSPE3/report/WSSSPE3_review.tex
done with participants
Former-commit-id: f35b1beca166d8fb50eea687378e71b0a1f8f0af

\include{wg_main_best_practices}
\include{wg_main_catalogs}
\include{wg_main_eng_design}
\include{wg_main_funding_spec_expert}
\include{wg_main_funding_spec_expert}
\include{wg_main_industry_interaction}
\include{wg_main_industry_interaction}
\include{wg_main_legacy_SW}
\include{wg_main_metrics}
\include{wg_main_publishing_SW}
\include{wg_main_software_credit}
\include{wg_main_training}
\include{wg_main_user_community}

@@

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Attendees}  \label{sec:attendees}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{need to update for WSSSPE3}
The following is a partial list of workshop attendees who registered on the
collaborative notes document~\cite{WSSSPE2-google-notes} that was used
for shared note-taking at the meeting, or who participated in a breakout groups
and were noted in that group's notes.

@@

>>>>

\input{wg_main_best_practices}
\input{wg_main_funding_spec_expert}
\input{wg_main_catalogs}
\input{wg_main_industry_interaction}
\input{wg_main_legacy_SW}
\input{wg_main_eng_design}
\input{wg_main_metrics}
\input{wg_main_training}
\input{wg_main_software_credit}
\input{wg_main_publishing_SW}
\input{wg_main_user_community}

@@

\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Attendees}  \label{sec:attendees}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The following is list of participants registered for the WSSSPE3 workshop.

@@

\input{wg_appendix_best_practices}
\input{wg_appendix_funding_spec_expert}
\input{wg_appendix_catalogs}
\input{wg_appendix_industry_interaction}
\input{wg_appendix_legacy_SW}
\input{wg_appendix_eng_design}
\input{wg_appendix_metrics}
\input{wg_appendix_training}
\input{wg_appendix_software_credit}
\input{wg_appendix_publishing_SW}
\input{wg_appendix_user_community}
